Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-16 Paper2015.tex
Add eps and png files
Updated authors to include Elke.
working process

\author{Q. Hong,
S. P. Platt,~\IEEEmembership{Member,~IEEE}
Alexander V. Prokofiev,~\IEEEmembership{Member,~IEEE}
\thanks{further information}\\[2mm] 	% Your name
%\normalsize University of Central Lancashire \\ 							% Your institution
%\normalsize \href{qhong@uclan.ac.uk} 								% Your email address
\vspace{-5mm}
}

@@

\begin{figure}[t]
    \vspace{2in}
%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{ANITAIntYieldRADECS.eps}\hspace{\columnwidth}}\\
    \vspace{2in}
%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{ANITALetYieldnormalisedRADECS.eps}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}

>>>>

\author{Q. Hong,
S. P. Platt,
A. V. Prokofiev,
E. Passoth
\thanks{further information}\\[2mm] 	% Your name
%\normalsize University of Central Lancashire \\ 							% Your institution
%\normalsize \href{qhong@uclan.ac.uk} 								% Your email address
\vspace{-5mm}
}

@@

\begin{figure}[t]
    \vspace{2in}
%	\subfloat[Integral fluence rate]{\todo{Integral spectra on log-log axes}\hspace{\columnwidth}}\\
	\subfloat[Integral fluence rate]{\includegraphics[width=3in]{SUPcomparedIFluxRADECS.eps}\hspace{\columnwidth}}\\
    \vspace{2in}
%	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\todo{Normalised spectra on lethargy axes}\hspace{\columnwidth}}
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\includegraphics[width=3in]{SUPNormalisedRADECS.eps}\hspace{\columnwidth}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:SUPSpectraComparison}
\end{figure}
